An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-15 main.tex
Improve tables Addresses #35
- Rewrite appendix with player information.
- Simplify the tables of top performing strategies.
- Present top 10% of strategies as opposed to top 5.
- Make TF* appear in bold.
- Include lines to separate strategies in rank tables and also display ints

To carry out this large numerical experiment, \input{./tex/num_strategies}
strategies, listed in Appendix~\ref{app:list_of_players} are used library. There
are \input{./tex/num_stochastic.tex}stochastic and
\input{./tex/num_deterministic.tex}deterministic strategies. Their memory depth,
defined by the number of rounds of history used by the strategy each round, is
shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
strategy uses the entire history of play (whatever its length). For example, a
strategy that utilizes a handshaking mechanism where the opponents actions on
the first few rounds of play determines the strategies subsequent behavior would
have infinite memory depth.

@@

For \(N=2\) the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in sections~\ref{sec:strong_invaders} and
~\ref{sec:strong_resistors}.  Figure~\ref{fig:boxplot_2} shows all fixation
probabilities for the strategies considered. This is summarised in
Table~\ref{tbl:summary_top_2}.

@@

\begin{table}[!hbtp]
    \centering
    \input{./tex/summary_top_2_invade.tex}
    \caption{Summary of top five strategies for \(N=2\) (neutral fixation is $p=0.5$.}
    \label{tbl:summary_top_2}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/boxplot_3_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
    \label{fig:boxplot_3_invade}
\end{figure}

@@

The top five strategies are given in Tables~\ref{tbl:top_five_invade}.

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_14_invade.tex}
        \caption{\(N=14\)}
    \end{subfigure}
    \caption{Properties of top five invaders}
    \label{tbl:top_five_invade}
\end{table}

@@

As well as noting that the memory length and complexity of these strategies are
much greater than one, it is interesting to note that none of them are akin to
memory one strategies. Only one is stochastic although close inspection of the
source code of PSO Gambler shows that it makes stochastic decisions rarely, and
is functionally very similar to its deterministic cousing EvolvedLookerUp. Apart
from TF3 in \(N=3\), the finite state machines trained specifically for Moran
processes do not appear in the top 5: whereas strategies trained for tournament do.
This is due to the nature of invasion: most of the opponents will initially be different
strategies. The next section will consider the converse situation.

@@

Table~\ref{tbl:top_five_resist} shows the top five strategies when ranked
according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\).
Once again none of the short memory strategies from
Section~\ref{sec:two_individuals} perform well for high \(N\).

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_14_resist.tex}
        \caption{\(N=14\)}
    \end{subfigure}
    \caption{Properties of top five resistors}
    \label{tbl:top_five_resist}
\end{table}

@@

All source code for this work has been written in a sustainable manner: it is
open source, under version control and tested which ensures that all results can
be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
% TODO Add reference to source code
the processed data has also been properly archived and can be fond
at \cite{data}.

@@

\begin{multicols}{3}
	\begin{enumerate}
		\input{./tex/list_of_players.tex}
	\end{enumerate}
\end{multicols}

>>>>

To carry out this large numerical experiment, \input{./tex/num_strategies}
strategies, listed (with their properties) in Appendix~\ref{app:list_of_players}
are used library. There are \input{./tex/num_stochastic.tex}stochastic and
\input{./tex/num_deterministic.tex}deterministic strategies. Their memory depth,
defined by the number of rounds of history used by the strategy each round, is
shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
strategy uses the entire history of play (whatever its length). For example, a
strategy that utilizes a handshaking mechanism where the opponents actions on
the first few rounds of play determines the strategies subsequent behavior would
have infinite memory depth.

@@

For \(N=2\) the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
probabilities for the strategies considered. This is summarised in
Table~\ref{tbl:summary_top_2}.

@@

\begin{table}[!hbtp]
    \scriptsize
    \centering
    \input{./tex/summary_top_2_invade.tex}
    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\).}
    \label{tbl:summary_top_2}
\end{table}

@@

\begin{figure}[!hbtp]
    \scriptsize
    \centering
    \includegraphics[height=.9\textheight]{./img/boxplot_3_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
    \label{fig:boxplot_3_invade}
\end{figure}

@@

The top strategies are given in Tables~\ref{tbl:top_five_invade}.

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{./tex/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{./tex/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \input{./tex/summary_top_14_invade.tex}
        \caption{\(N=14\)}
    \end{subfigure}
    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
    \label{tbl:top_five_invade}
\end{table}

@@

As well as noting that the memory length and complexity of these strategies are
much greater than one, it is interesting to note that none of them are akin to
memory one strategies. Only one is stochastic although close inspection of the
source code of PSO Gambler shows that it makes stochastic decisions rarely, and
is functionally very similar to its deterministic cousin EvolvedLookerUp. Apart
from TF3 in \(N=3\), the finite state machines trained specifically for Moran
processes do not appear in the top 5: whereas strategies trained for tournaments do.
This is due to the nature of invasion: most of the opponents will initially be different
strategies. The next section will consider the converse situation.

@@

Table~\ref{tbl:top_five_resist} shows the top strategies when ranked
according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\).
Once again none of the short memory strategies from
Section~\ref{sec:two_individuals} perform well for high \(N\).

\begin{table}[!hbtp]
    \scriptsize
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{./tex/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{./tex/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \input{./tex/summary_top_14_resist.tex}
        \caption{\(N=14\)}
    \end{subfigure}
    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
    \label{tbl:top_five_resist}
\end{table}

@@

All source code for this work has been written in a sustainable manner: it is
open source, under version control and tested which ensures that all results can
be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
% TODO Add reference to source code
the processed data has also been properly archived and can be found
at \cite{data}.

@@

\begin{multicols}{2}
	\begin{enumerate}
		\input{./tex/list_of_players.tex}
	\end{enumerate}
\end{multicols}
